Weed and Corn segmentation through Convolutional Neuronal Networks

### 2017-06-01 PaperBCJ.tex
Add matherials and methods

\section{Matherial and Methods}
%Codigo para la Implementacion del Algoritmo
The development of the model for the weed and maize detection algorithm using convolutional neural networks is described below.
\\
\subsection{Hardward}
The card used is a Raspberry Pi 3. The camera used for both the sampling and the model was a RaspBerry Pi Camera module v2, 		which is configured to obtain a video at a resolution of 640 by 480 pixels , In order to improve the performance of image 	processing.
\\

@@

The programs / packages used were OpenCV and Qt, for the acquisition, segmentation of images, Cafe for the realization of neural networks,
\\
\subsection{Neural networks}
For the training of neural networks we used an AlexNet architecture, but we do quizes with others architectures like Let Net, Inception Ned, but the results wont good.
\\
\subsection{Dataset Desciption}
	\begin{figure}[!t]
	For the model we have two categories, the first maize in its initial stage, and the second weed, All images for the dataset were obtained from maize cultivations in their initial stage in Pillaro canton, where they had a total of  2225 images, of which 1622 images were of maize and 603 of weed, once obtained the images are processed by openCV to segment them and can be obtained as follows:
	\\

	\centering
	\includegraphics[width=2.5in]{im1}
	\caption{Simulation results for the network.}
	\label{fig_sim}

	\subsection{Convolutional Neuronal Network}
	After the segmentation of the pictures have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{Razavian}. Their are also applied in Precision Agriculture \cite{Potena:Nardi} for the correct identification of plants. 
	\section{Test}
	%Codigo para la Implementacion del Algoritmo

@@

>>>>

\section{Matherials and Methods}
The development of the model for the weed and maize detection algorithm using convolutional neural networks is described below.
\\
\subsection{Hardware}
For the stages of obtaining images and training net we  used the following elements: A Raspberry Pi 3 with Pi Camera V2.1 for the record of images, it was configured to obtain a video at a resolution of 640x480 pixels in order to improve the performance of image processing. Due to the popularity of the GPU computing, it was neccesary to consider hardware compatible with Parallel Computing like the Graphic Cards manufactured by NVIDIA, they have the advantage of better times of processing compared to CPU, in order to optimize the time of image processing and training of Deep Learning Models, so we used a Computer with a Nvidia Graphics Card GTX950M.
\\

@@

For the application in this documents requires the use of powerful libraries of Image Processing and Deep Learning Development, we considered to use Open Software for extend its use  in future prototypes, due to this considerations we had chosen the OpenCV library for its computational efficiency and focus on real-time application \cite{OpenCV} in this  case, it was used for acquisition and segmentation of the sample images. Also we had considered Caffe because it is intended to use in training and developing general-purpose Convolutionals Neural Networks and other Deep Lerning models \cite{caffe} with fully support of CUDA GPU Computation and a generous database of resources for learning,	
\\

Also in the development stage was important the use of Linux OS , its features are: lightweight and free OS also fully compatible with the software mentioned above. For the main computer was used Ubuntu Linux 16.04 for its official support to CUDA, Caffe and OpenCV, also in the Raspberry Pi we used the Pixel OS for acquire images and processing of the CNN.
\\

\subsection{Dataset Description}
Due to the lack of datasets of Weed and Maize plants, it was neccesary to search crops of maize in its initial stage, for that purpose we had traslated to P\'illaro, it is a city located in the Tungurahua Province on the center of the  the Ecuadoring Highlands region, P\'illaro is recognized producer of Andean Crops such as: Maize, Potatoes and Fruits so here we could find many crops of Maize useful for our purpose. \\

Samples were obtained from images captured in those maize fields , we considered to choose Maize Crops where we could visually discriminate the plants of the crop and the weed.  To record the samples we centered the camera insuring that the capture shows all the features of the maize plant, it was possible by monitoring the get of samples by an external display. An examples of the images captured are shown below. 
\\

	\begin{figure}[h]
	\centering
	\includegraphics[width=3.2in]{entradamaiz}
	\caption{Crops chosen to obtain samples, notice that it is easy to discrimante weed from maize}
	\label{fig_sim}
	\end{figure}

Then, through a digital image processing, the images were segmented to differentiate them from the soil and other non-plant elements, then the images were masked to provide the dataset features of color of the Maize and Weed. Once the segmented images were obtained, they were removed those that had a resolution lower than 64x64 pixels, because it's smaller than size of input layer of the network, besides it was not convenient its processing since its total area was much smaller than the samples of corn, which is the purpose of this document. To highlight we had labelled the samples manually in two classes. In the following image we present the final results of the processed images that conform the dataset.

	\begin{figure}[h]
	\centering
	\includegraphics[width=2.5in]{im1}
	\caption{ Segmented and Masked images of dataset Above: Weed, Below: Maize}
	\label{fig_sim}
	\end{figure}

Once we completed the processing of the images were obtained 2369 images of Maize and 632 images of Weed, \textbf{Seng} \cite{SengChang} said that once CNN has reached an acceptable accuracy, the dataset could extend by Geometric Transformations, because we will develop a  system  for classify the maize in any position , we considered to rotate the source sample to 90º,180º and 270º so the dataset will be treble, improving the accuracy of the model. \\

For the Validation Phase, we had chosen randomly a fifth part of the total images of each class, so we have the following chart with the distribution of the dataset.

\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c||} 
 \hline
 Phase & Train & Validation & Test & Total \\ [0.5ex] 
 \hline\hline
 Maize & 7581 & 1895 & 787 & 9476 \\ 
 Weed & 2023 & 505 & 300 & 2528\\[1ex] 
 \hline
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}

\subsection{Convolutional Neuronal Network}
	After the last step have been terminated, it is neccesary classify the images of Maize and Weed, a high accurate method of Image Classification is Convolutional Neuronal Networks(CNN), those models are complex but efficient with a highly rate of discrimination and its demostrated that they have good results in Image Classification, Object Detection and Fine-Grained  Classification \cite{Razavian}. Their are also applied in Precision Agriculture \cite{Potena:Nardi} for the correct identification of plants.
\\

One of the characteristics of the CNN is that they can have multiple architectures, each architecture can reach different result depending of the application , for the present document we have considered four CNN architectures: Two models were chose of the Caffe Zoo Model(it's a free resource provided by Caffe Developers), LeNet and AlexNet also Potena and Nardi had used two additional types of Models, sNET and cNET, they were sucessfully proved in identification of plants in crops\cite{Potena:Nardi}, with the Nets chosen, each one was trained with a same Solver of type AdaDelta and with the same dataset, the results of training are the following. 
\\
\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c||} 
 \hline
 Parameters & LeNet & AlexNet & cNET & sNET \\ [0.5ex] 
 \hline\hline
 Input size of images & 32x32 & 64x64 & 64x64 & 64x64 \\ 
 Layers numbers & 9 & 11 & 8 & 4\\
 Number of parameters & 652500 & 20166688 & 6421568 & 135872 \\ 
 Iterations & 3000 & 3000 & 4500 & 3000 \\ 
  Accuracy(\%) & 78.84 & 95.266 & 99.33 & 90.4 \\
  Loss(\%) & 44.8471 & 12.7256 & 5.86 & 781.3 \\ [1ex] 
 \hline
\end{tabular}
\caption{Distribution of the Dataset of each class}
\label{table:1}
\end{table}

Inside of the shown parameters in the Table {table:1}, we considered the net who achieved the highest rate of accuracy and lowest rate of loss, clearly the cNET is the chosen due it shows a precission equal to human classification. The following picture shows the process of training of the cNET \\

	\begin{figure}[h]
	\centering
	\includegraphics[width=3.5in]{entrenamiento}
	\caption{ Left: Accuracy vs Iterations, Right: Loss vs Iterations}
	\label{fig_sim}
	\end{figure}

	\section{Test}
	%Codigo para la Implementacion del Algoritmo

@@

   \bibitem{OpenCV}
 A. S. ~Razavian, C. ~Potena, G. ~Grisetti and A.~Pretto, \emph{CNN Features off-the-shelf: an Astounding Baseline for Recognition} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2017.

     \bibitem{caffe}
Jia, Yangqing and Shelhamer, Evan and Donahue, Jeff and Karayev, Sergey and Long, Jonathan and Girshick, Ross and Guadarrama, Sergio and Darrell, Trevor, \emph{Caffe: Convolutional Architecture for Fast Feature Embedding} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2014.

       \bibitem{SengChang}
Seng Chang \emph{Caffe: Convolutional Architecture for Fast Feature Embedding} Vol ~143 Issue 2 \hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: IEE Proceedings - Vision, Image and Signal Processing, 2014.
